What's in a Domain? Anaylsis of URL Features

### 2023-06-18 paper/acm_paper.tex
Reworked paper for confernce submission

For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
that the feature was derive from, using Figure \ref{fig:url} as a guide to these segments. 
We sum the feature importance for all features within a URL segment to allow us to plot the
segment contributions to model performance. We provide a thin grey coloured line covering the entire segment
which captures the importance of global features (like URL length). If the script is applied to a dataset with
more than just URL features then all non-URL fetaures would be grouped into this global group. All segment specific
URL features are plotted below their segment in a canonical example URL.

>>>>

For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
that the feature was derived from, using Figure \ref{fig:url_structure} as a guide to these segments. 
We sum the feature importance for all features within a URL segment to allow us to plot the
segment contributions to model performance. We provide a thin grey coloured line covering the entire segment
which captures the importance of global features (like URL length). If the script is applied to a dataset with
more than just URL features then all non-URL fetaures would be grouped into this global group. All segment specific
URL features are plotted below their segment in a canonical example URL.
